---
title: "Child Care"
output:
  html_document:
    number_sections: no
    theme: sandstone
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---
<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
 body{
  font-family: Franklin Gothic;
}
</style>


```{r setup, include=FALSE} 

knitr::opts_chunk$set(comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE
)

setwd("W:/Project/RDA Team/First5LA/V2.0 Report/R")

library(ggplot2)
library(dplyr)
library(stringr)
library(RPostgreSQL)
library(tidyr)
library(scales)
library(knitr)
library(data.table)
library(sp)
library(sf)
library(rgdal)
library(rpostgis)
library(highcharter)
library(kableExtra)
library(tigris)

# Data Setup
pw <- {
  "password"
}
# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")

con <- dbConnect(drv, dbname = "f5la_v2",
                 host = "aws-postgres-db.c5udgz7ro8hq.us-west-2.rds.amazonaws.com", port = 5432,
                 user = "postgres", password = pw)

```


```{r, include=FALSE}

####### ESTABLISH HIGHCHART THEME ############


##colors as a vector

cols=c("#033E8C", "#EC098D", "#04B2D9","#26BFB0", "#64BF4B")

cols3=c("#EC098D", "#04B2D9",   "#033E8C")

cols9=c("#04B2D9", "#033E8C", "#EC098D","#26BFB0", "#64BF4B", "#590219","#D9C71A", "#11768C","#04B2D9")

####MAKE MY HC THEME###

  thm <- hc_theme(
  colors = c("#033E8C", "#EC098D", "#04B2D9","#26BFB0", "#64BF4B"),
  chart = list(
    backgroundColor = ""
  ),
  title = list(
    style = list(
      color = "#333333",
      fontFamily = "Franklin Gothic Condensed"
    )
  ),
  subtitle = list(
    style = list(
      color = "#666666",
      fontFamily = "Franklin Gothic"
    )
  ),
  legend = list(
    itemStyle = list(
      fontFamily = "Franklin Gothic",
      color = "black"
    ),
    itemHoverStyle = list(
      color = "gray"
    )
  )
)


```

# Program Officer and Grantee Perspectives

<br>

*	The pandemic forced schools and child care centers to close, resulting in children having nowhere to go outside of their homes. This created a greater dependence on virtual tools, such as video conferencing and wifi access, to ensure that children can engage in remote classes or activities.
*	Greater reliance on technology has revealed the digital divide that exists. Many families in Best Start geographies do not have access to wifi or laptops needed to enroll children in remote programs.
*	Children are having a harder time staying engaged during the day which can hurt educational outcomes.
*	This indicator is similar to the Impact Framework's child care indicator. Progress on this indicator helps achieve [<nobr style="color: #26BFB0;">__First 5 LA’s Result: Early Learning.__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74){target="_blank"}
* [Additional stories directly from providers about their experiences providing early learning and care for families during the pandemic](https://www.advancementprojectca.org/blog){target="_blank"}

# Policy Opportunities {.tabset .tabset-pills}

## Infrastructure to Support Children and Families

* __Provide immediate financial support for home-based and center-based early educators adapting to COVID-19 guidelines to sustain the viability of serving children of essential workers.__ Allocate funding to guarantee full reimbursement for providers impacted by COVID-19 to stabilize the early learning and care field as many have been forced to close. Provide incentives and stipends to help providers cover increased program costs arising from reduced teacher-child ratios, rearranging their environments to respond to safety regulations, and increasing the supply of sanitizing and disinfecting materials. . [<nobr style="color: #26BFB0;">__F5LA Result: Early Learning__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74){target="_blank"}

## Direct Services and Technical Support

* __Prioritize funding and linguistically accessible information/training/professional development for providers of dual-language early learning and care programs, particularly for monolingual providers of a language other than English.__ Children of essential workers are predominantly from families of color with languages other than English. Culturally and linguistically responsive dual language programs provide the foundation for overall language, cognitive, and healthy identity development.   [<nobr style="color: #26BFB0;">__F5LA Result: Early Learning__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74){target="_blank"}
* __Provide funding and training for providers to support virtual learning and technology needs of essential workers’ young children and school-aged students.__ As school districts engage in distance/hybrid learning, families are looking to after-school providers for full-day care. Providers need funding to be able to hire an assistant to support distance learning as they serve school-aged children alongside young children in their care.  [<nobr style="color: #26BFB0;">__F5LA Result: Early Learning__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74){target="_blank"}

# Data

## Child Care Workers in Best Start Geographies

Child care workers are more numerous in Best Start geographies relative to the rest of the county, as indicated in the darker shading of purple. This makes it more important than ever that child care workers are getting sufficient resources and support in order to then take care of children in these communities. While a high number and percentage of child care workers preside in Best Start Geographies, stay-at home orders and safety concerns are driving [child care center closures](https://jzhang514.github.io/f5la/Childcare-Center-Closures.html){target="_blank"}, which impacts both child care workers and  working families who need child care for their children.

<br>
<p class="round1">__Why this matters:__ [Child care providers are predominantly immigrant women of color](https://www.advancementprojectca.org/blog/state-and-local-resources-to-support-early-learning-and-care){target="_blank"}, and they need more support and resources to ensure they can provide child care for families while maintaining their own safety. Stay-at-home orders and safety regulations make it even harder for providers to earn income, further exacerbating the disparities income disparities in the education field. Supporting the safety and capacity of child care workers subsequently supports families with child care needs.</p>

<br>
Please note that child care workers age 16 to 18 are currently included in this analysis and can be excluded as needed.<br> 

```{r}

#######################CHILD CARE MAP W/ CPER DATA#####################################

##Original R Script:"W:\Project\RDA Team\First5LA\V2.0 Report\R\Essential Workers_CEPR Data.R"

#read in CEPR data

cepr_lac <- dbGetQuery(con, "SELECT * FROM cepr_lac")

#create dataframe subsetting only for
#employed childcare workers and 
#aggregating the person weights for child care workers, and everyone in the dataset

cepr_lac_childcare<-cepr_lac%>%filter(flind1=='6' &
         flind_dd=='SCA-Child Day Care Services' &
         socp18=='PRS-Childcare Workers' &
         lfstat == 'Employed')%>%
  group_by(socp18, puma10)%>%
  summarise(childcare_tot=sum(perwgt))%>%
  mutate(pop_tot=10098376)%>% #got this number by summing the person weight of the entire dataset
  mutate(geoid10=paste0('060', puma10)) #create new puma column that includes the leading '06' for joining 


#read in puma spatial file
puma<-pgGetGeom(con, "puma_lac") #get la county pumas that I created in postgres by filtering on geoid10 ilike '06037%'

#join the puma spatial data to the childcare data on geoid10
cepr_lac_childcare<-merge(puma, cepr_lac_childcare, duplicateGeoms = TRUE, all=TRUE)


#transform for leaflet
cepr_lac_childcare<-spTransform(cepr_lac_childcare, CRS('+proj=longlat +datum=WGS84'))

######Layer 2: BSC###########

bsc<-pgGetGeom(con, "f5la_best_start_geographies") #this is the updated view that CR made 

#convert to sf 
bsc<-st_as_sf(bsc)

####transform bsc shapefile for leaflet

bsc<-st_transform(bsc, CRS('+proj=longlat +datum=WGS84'))

####Add XY coordinates to bsc spatial df

## find centroid coordinates
bsc_cnt = st_centroid(bsc)
bsc_crd = data.frame(st_coordinates(bsc_cnt))

#add ID column to each df and spatial df for joining
bsc$ID <- seq.int(nrow(bsc))
bsc_crd$ID <- seq.int(nrow(bsc_crd))

##join spatial frame with data frame to get the XY columns into the spatial frame

bsc<-geo_join(bsc, bsc_crd, 'ID', 'ID',
              how = "left")

#create label 
bsc_label<-paste(bsc$best_start)


#########################MAP###############################




######Define color palette and bins for map#######
library(leaflet)
library(RColorBrewer)

pal <- colorNumeric("PuRd",  domain = cepr_lac_childcare$childcare_tot)
#mybins <- c(0,10,20,50,100,500,Inf)


#######Map#########




leaflet(cepr_lac_childcare)%>%
  
  addMapPane("puma_pane", zIndex=485)%>%
  addMapPane("bsc_pane", zIndex=490)%>%
 
  
  #puma layer
  
  addPolygons(data=cepr_lac_childcare, weight = .40, color="black", smoothFactor = 0.8,
              opacity = 1, fillColor=~pal(childcare_tot), fillOpacity = .75,
              highlight=highlightOptions(color= "white", stroke = 1.5, weight = 2, bringToFront = TRUE), 
              popup = ~paste0(cepr_lac_childcare$name10, "</br>", "Total Child Care Workers: ",cepr_lac_childcare$childcare_tot),
               options = pathOptions(pane = "puma_pane")
              )%>%
  
  #bsc layer
  
  addPolygons(data=bsc, color="black", weight=2, opacity = 1, fill=F,
              label=as.character(bsc$best_start),
               options = pathOptions(pane = "bsc_pane")) %>%
  addLabelOnlyMarkers(data=bsc,  ~X, ~Y, label =  ~as.character(bsc_label), 
                      labelOptions = labelOptions(noHide= T, direction = 'top', textOnly = T,
                                                  style=list("font-size"="8px", "color"="black",  "font-weight" = "bold")))%>%
  
  
  #base and view
  addProviderTiles("CartoDB.PositronNoLabels")%>%
  setView(	-118.205914, 	34.187684	, zoom = 9)%>%
  
  #legend
  addLegend("bottomright", pal=pal, values = ~childcare_tot,
            title = "Child Care Workers Living<br>in Best Start Geographies")
  



```
Source: [Center for Economic and Policy Research Analysis of American Community Survey, 2014-2018 5-Year Estimate](https://github.com/ceprdata/frontline-workers){target="_blank"}

<br>
<a href="https://jzhang514.github.io/f5la/Childcare-Center-Closures.html" class="button" target="_blank">Click here to explore more about Child Care Closures</a>

<br>

## The Digital Divide {.tabset .tabset-pills}

In light of the pandemic, it is unsurprising that access to __internet and the digital divide__ has risen in importance. All Program Officers and Regional Network Grantees expressed the importance of digital equity in being able to outreach to families and for child care and education needs. 

### Internet Access

This graph looks at the percentage of families who have Broadband such as cable, fiber optic or DSL in their homes. Families must have this type of internet in order to use virtual tools such as Zoom. It is important to distinguish the type of internet families have, because if a family has basic internet but cannot access video conferencing platforms that are commonly used, then that contributes to the widening digital divide. __In Broadway/Manchester, East LA and Watts/Willowbrook, less than half of the families living in these communities do not have the internet access needed for videoconferencing.__

```{r}

#############Internet Access#################

internet<-dbGetQuery(con, "SELECT * FROM f5la_2021_internet")%>%
  filter(!grepl("LA County", best_start))%>%
   mutate(tot_broadband = as.character(formattable::comma(tot_broadband, 0)))%>%
     mutate(tot_oneormoredevice = as.character(formattable::comma(tot_oneormoredevice, 0)))


#highcharts

hchart(internet, "column",
         hcaes(x=best_start, y=pct_broadband),
          tooltip = list(pointFormat = "Percentage of Households with Internet: {point.pct_broadband:.1f}%<br>
                         Number of Households with Internet: {point.tot_broadband}"))%>%

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""), 
             labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=100,
       plotLines = list(
      list(
        label = list(text = "LA County = 71.46%<br>", align = "left"),
        color = "#FF0000",
        width = 2,
        value = 71.46
      )
    ))%>%
    hc_title(
    text = "Homes with Broadband Internet Access such as Cable, Fiber Optic or DSL",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://data.census.gov/cedsci/">ACS 2019 5-Year Estimates (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE)%>%

hc_add_theme(thm)%>%
  hc_exporting(
    enabled = TRUE, sourceWidth=900, sourceHeight=600, chartOptions=list(subtitle=NULL),
    filename = "plot"
    )



# #create factors for the x axis labels (bsc) to customize the order
# internet$best_start <-  factor(internet$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# 
# cols<-c( "#FF6666", "#FF6666", "#FF6666","#FF6666", "#FF6666", "#FF6666","#FF6666","#FF6666","#FF6666",
#          "#FF6666","#FF6666","#FF6666","#FF6666","#FF6666")

#ggplot graph

# ggplot(internet, aes(y=pct_internet/100, x=best_start))+
#   geom_bar(stat="identity", fill = cols)+ 
#   geom_hline(yintercept=.824, linetype="dashed")+ #y intercept is the total rate which you can find on rc site, pgadmin, or from earlier table prior to filtering
#   geom_text(data=data.frame(x=0,y=.824), aes(x, y), label="LA County Rate = 82.4%",  vjust=-.5, hjust=-.1)+ 
#    scale_y_continuous(name="", limits = c(0, 1), labels=percent)+
#   scale_x_discrete(name="")+
#   theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         legend.title = element_blank())+
#   ggtitle("Homes with Internet Access in the Best Start Geographies")


``` 

<p class="round1">__Why this matters:__ With the pandemic forcing massive closures, families and children began having to rely on the internet to access a host of social resources. Children living without internet access will incur more learning loss; a disparity in digital access is driving a widening disparity in education outcomes. Several social welfare programs also transitioned to remote access as stay-at-home orders came into effect. Unfortunately, the families who likely need social assistance most are also least likely to have internet access, widening the gap between those who need and those who can access those resources.</p>
<br>

### Families who Own One or More Technology Devices

Remote learning and child care requires families to have reliable internet as well as sufficient devices for all the children and adults who are learning or working remotely from home. The visual below shows the percentage of families who own at least one or more devices at home.


```{r}

#highcharts

hchart(internet, "column",
         hcaes(x=best_start, y=pct_oneormoredevice),
          tooltip = list(pointFormat = "Percentage of Homes w/ One or More Device: {point.pct_oneormoredevice:.1f}%<br>
                         Number of Households w/ One or More Device: {point.tot_oneormoredevice}"))%>%

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""), 
             labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=100,
       plotLines = list(
      list(
        label = list(text = "LA County =92.0%<br>", align = "left"),
        color = "#FF0000",
        width = 2,
        value = 92.0
      )
    ))%>%
    hc_title(
    text = "Families who own One or More Technology Devices",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://data.census.gov/cedsci/">ACS 2019 5-Year Estimates (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE)%>%

hc_add_theme(thm)%>%
  hc_exporting(
    enabled = TRUE, sourceWidth=900, sourceHeight=600, chartOptions=list(subtitle=NULL),
    filename = "plot"
    )



```

<br>
<p class="round1">__Why this matters:__ Families with multiple children, especially if one is a K-12 aged child and another is an age 0 to 5 child, might have a constraint on available technological devices in the home. It is more likely that families will prioritize giving a K-12 aged child access to a device for online school purposes, resulting in a child age 0 to 5 foregoing access. This results in children age 0 to 5 not being able to access early learning care and engagement, which can impact their educational journey in future years.</p>
<br>

### Families with Age 0 to 5 Child and a K-12 Aged Child
```{r}

children<-dbGetQuery(con, "SELECT * FROM f5la_2021_multiplechildren")



#separate the estimate and percents to separate columns then recombine 

children_num<-gather(children, num_measure, num_value,  tot_hh:pct_hh_childund6_6to17, factor_key=TRUE)%>%
  filter(grepl("est", num_measure))%>%mutate(num_value = as.character(formattable::comma(num_value, 0)))


children_pct<-gather(children, pct_measure, pct_value,  tot_hh:pct_hh_childund6_6to17, factor_key=TRUE)%>%
  filter(grepl("pct", pct_measure))

#combine pct and number dfs
children_long<-cbind(children_num, children_pct)
       

#remove duplicate name  column (best_start)
children_long<-children_long[c(-4)]


#highcharts

 children_long %>%
   mutate(variable=ifelse(pct_measure %in% 'pct_hh_childund6', 'Children Under 6 Years Old', 'Children 6-17 Years Old'))%>%
  hchart('column', hcaes(x = 'best_start', y = 'pct_value', group = 'variable'),
          tooltip = list(pointFormat = "Percent: {point.pct_value:,.1f}%<br>
                        Total: {point.num_value}")) %>%
   hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale", "LA County"))%>%
    hc_yAxis(title = list(text = ""), 
             labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=40)%>%
    hc_title(
    text = "Families with Age 0 to 5 and K-12 Aged Children",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://data.census.gov/cedsci/">ACS 2019 5-Year Estimates (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE,
               itemDistance= 100)%>%
 hc_add_theme(thm)%>%
  hc_exporting(
    enabled = TRUE, sourceWidth=900, sourceHeight=600, chartOptions=list(subtitle=NULL),
    filename = "plot"
    )
  




```

## Pre-K Early Learning Care Enrollment

The difference between the numbers of pre-k children who are eligible for subsidized early learning care programs versus enrolled in them is significant. This highlights the need to improve outreach and understand the barriers preventing eligible families from enrollment.<br>

```{r}

#####prek

#grab data
prek<-dbGetQuery(con, "SELECT * FROM bsc_unmet_ece_prek_new")%>%
  select(1,3:6)


#convert data wide to long and prep for graphing

prek_long <- melt(setDT(prek), id.vars = c("best_start"), variable.name = "type")%>%
  filter(!grepl("unmet_need", type))%>%
  filter(!grepl("LA County", best_start))%>%
  mutate(variable = ifelse(type %in% 'eligible_children_prek', 'Eligible Children', 'Enrolled Children'))%>%
  mutate(valuelabel=as.character(formattable::comma(value, 0)))


                     
#highcharts
hchart(prek_long, type="column",
         hcaes(x=best_start, y=value, group=variable),
          tooltip = list(pointFormat = "{point.variable}: {point.valuelabel}"))%>%
       #hc_plotOptions(series = list(stacking = "normal"))%>%
      hc_tooltip(crosshairs = TRUE)%>%
  

     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""))%>%
    hc_title(
    text = "Pre-K Eligibility and Enrollment in Subsidized Early Learning Care Programs",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://elneedsassessment.org/">Early Learning Needs Assessment Tool, American Institutes for Research (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE,
               itemDistance= 50)%>%
hc_add_theme(thm)%>%
  hc_exporting(
    enabled = TRUE, sourceWidth=900, sourceHeight=600, chartOptions=list(subtitle=NULL),
    filename = "plot"
    )

# #create factors for the x axis labels (bsc) to customize the order
# prek_long$best_start <-  factor(prek_long$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# 
# #graph
# 
# ggplot(prek_long, aes(fill=type, y=value, x=best_start))+
#   geom_bar(position="stack", stat="identity")+
#    scale_y_continuous(name="", labels=comma, limits = c(0, 30000))+
#   scale_x_discrete(name="")+
#         theme(plot.title = element_text(hjust = 0.5), legend.position="right", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         plot.margin = margin(.1, .1, .1, .1, "cm"))+
#   scale_fill_discrete(labels=c("Total", "Eligible", "Enrolled"))+
#   labs(fill="")+
#     ggtitle("Pre-K Eligibility and Enrollment in Subsidized \nEarly Learning Care Programs")
  

#graph LA County or make table???

# prek_la<-melt(setDT(prek), id.vars = c("bsc"), variable.name = "type")%>%
#   filter(grepl("LA County", bsc))
```
<br>Source: [Early Learning Needs Assessment Tool, American Institutes for Research](https://elneedsassessment.org/){target="_blank"}

## Infant Toddler Early Learning Care Enrollment

The gap between infant toddlers who are eligible for subsidized early learning programs versus enrollment in them is substantial. Enrollment if extremely low across Best Start geographies. The gap for infant toddlers is larger than the gap among pre-k children, making this a higher priority area.<br>

```{r}

#grab data
it<-dbGetQuery(con, "SELECT * FROM bsc_unmet_ece_it_new")%>%
  select(1,3:6)


#convert data wide to long and prep for graphing
it_long <- melt(setDT(it), id.vars = c("best_start"), variable.name = "type")%>%
  filter(!grepl("unmet_need", type))%>%
  filter(!grepl("LA County", best_start))


#mutate and make the labels nicer for the legend on the graph

it_long<-it_long%>%
  mutate(variable = ifelse(type %in% 'eligible_children_it', 'Eligible Children', 'Enrolled Children'))%>%
  mutate(valuelabel=as.character(formattable::comma(value, 0)))

  

#highcharts graph
hchart(it_long, "column",
         hcaes(x=best_start, y=value, group=variable),
         #stacking="normal",
          tooltip = list(pointFormat = "Total: {point.valuelabel}"))%>%
      
      hc_tooltip(crosshairs = TRUE)%>%
  
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""))%>%
    hc_title(
    text = "Infant Toddler Eligibility and Enrollment in Subsidized Early Learning Care Programs",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://elneedsassessment.org/">Early Learning Needs Assessment Tool, American Institutes for Research (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE,
       itemDistance= 50)%>%
hc_add_theme(thm)%>%
  hc_exporting(
    enabled = TRUE, sourceWidth=900, sourceHeight=600, chartOptions=list(subtitle=NULL),
    filename = "plot"
    )


# #creat factors for the x axis labels (bsc) to customize the order
# it_long$best_start<- factor(it_long$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# #graph
# 
# ggplot(it_long, aes(fill=type, y=value, x=best_start))+
#   geom_bar(position="stack", stat="identity")+
#    scale_y_continuous(name="", labels=comma, limits=c(0, 30000))+
#   scale_x_discrete(name="")+
#         theme(plot.title = element_text(hjust = 0.5), legend.position="right", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         plot.margin = margin(.1, .1, .1, .1, "cm"))+
#   scale_fill_discrete(labels=c("Total", "Eligible", "Enrolled"))+
#   labs(fill="")+
#     ggtitle("Infant Toddler Eligibility and Enrollment in Subsidized \nEarly Learning Care Programs")


##if we want an LA only graph or table here ???

# it_la<-melt(setDT(it), id.vars = c("bsc"), variable.name = "type")%>%
#   filter(grepl("LA County", bsc))


```
<br>Source: [Early Learning Needs Assessment Tool, American Institutes for Research](https://elneedsassessment.org/){target="_blank"}
