---
title: "Child Care"
output:
  html_document:
    number_sections: no
    theme: sandstone
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
 body{
  font-family: Franklin Gothic;
}
</style>


```{r setup, include=FALSE} 

knitr::opts_chunk$set(comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE
)

setwd("W:/Project/RDA Team/First5LA/V2.0 Report/R")

library(ggplot2)
library(dplyr)
library(stringr)
library(RPostgreSQL)
library(tidyr)
library(scales)
library(knitr)
library(data.table)
library(sp)
library(sf)
library(rgdal)
library(rpostgis)
library(highcharter)
library(kableExtra)
library(tigris)

# Data Setup
pw <- {
  "password"
}
# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")

con <- dbConnect(drv, dbname = "f5la_v2",
                 host = "aws-postgres-db.c5udgz7ro8hq.us-west-2.rds.amazonaws.com", port = 5432,
                 user = "postgres", password = pw)

```


```{r, include=FALSE}

####### ESTABLISH HIGHCHART THEME ############


##colors as a vector

cols=c("#033E8C", "#EC098D", "#04B2D9","#26BFB0", "#64BF4B")

cols3=c("#EC098D", "#04B2D9",   "#033E8C")

cols9=c("#04B2D9", "#033E8C", "#EC098D","#26BFB0", "#64BF4B", "#590219","#D9C71A", "#11768C","#04B2D9")

####MAKE MY HC THEME###

  thm <- hc_theme(
  colors = c("#033E8C", "#EC098D", "#04B2D9","#26BFB0", "#64BF4B"),
  chart = list(
    backgroundColor = ""
  ),
  title = list(
    style = list(
      color = "#333333",
      fontFamily = "Franklin Gothic Condensed"
    )
  ),
  subtitle = list(
    style = list(
      color = "#666666",
      fontFamily = "Franklin Gothic"
    )
  ),
  legend = list(
    itemStyle = list(
      fontFamily = "Franklin Gothic",
      color = "black"
    ),
    itemHoverStyle = list(
      color = "gray"
    )
  )
)


```

# Program Officer and Grantee Perspectives

*	The pandemic forced schools and child care centers to close, resulting in children having nowhere to go outside of their homes. This created a greater dependence on virtual tools, such as video conferencing and wifi access, to ensure that children can engage in remote classes or activities.
*	Greater reliance on technology has revealed the digital divide that exists. Many families in Best Start geographies do not have access to wifi or laptops needed to enroll children in remote programs.
*	Children are having a harder time staying engaged during the day which can hurt educational outcomes.
*	This indicator is similar to the Impact Framework's child care indicator. Progress on this indicator helps achieve [<nobr style="color: #26BFB0;">__First 5 LA’s Result: Early Learning.__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)
* [Additional stories directly from providers about their experiences providing early learning and care for families during the pandemic](https://www.advancementprojectca.org/blog)

# Child Care Workers in Best Start Geographies

Child care workers are more numerous in Best Start geographies relative to the rest of the county, as indicated in the darker shading of purple. This makes it more important than ever that child care workers are getting sufficient resources and support in order to then take care of children in these communities. While a high number and percentage of child care workers preside in Best Start Geographies, stay-at home orders and safety concerns are driving [child care center closures](https://jzhang514.github.io/f5la/Childcare-Center-Closures.html), which impacts both child care workers and  working families who need child care for their children.

Please note that child care workers age 16 to 18 are currently included in this analysis and can be excluded as needed.<br> 

```{r}

#######################CHILD CARE MAP W/ CPER DATA#####################################

##Original R Script:"W:\Project\RDA Team\First5LA\V2.0 Report\R\Essential Workers_CEPR Data.R"

#read in CEPR data

cepr_lac <- dbGetQuery(con, "SELECT * FROM cepr_lac")

#create dataframe subsetting only for
#employed childcare workers and 
#aggregating the person weights for child care workers, and everyone in the dataset

cepr_lac_childcare<-cepr_lac%>%filter(flind1=='6' &
         flind_dd=='SCA-Child Day Care Services' &
         socp18=='PRS-Childcare Workers' &
         lfstat == 'Employed')%>%
  group_by(socp18, puma10)%>%
  summarise(childcare_tot=sum(perwgt))%>%
  mutate(pop_tot=10098376)%>% #got this number by summing the person weight of the entire dataset
  mutate(geoid10=paste0('060', puma10)) #create new puma column that includes the leading '06' for joining 


#read in puma spatial file
puma<-pgGetGeom(con, "puma_lac") #get la county pumas that I created in postgres by filtering on geoid10 ilike '06037%'

#join the puma spatial data to the childcare data on geoid10
cepr_lac_childcare<-merge(puma, cepr_lac_childcare, duplicateGeoms = TRUE, all=TRUE)


#transform for leaflet
cepr_lac_childcare<-spTransform(cepr_lac_childcare, CRS('+proj=longlat +datum=WGS84'))

######Layer 2: BSC###########

bsc<-pgGetGeom(con, "f5la_best_start_geographies") #this is the updated view that CR made 

#convert to sf 
bsc<-st_as_sf(bsc)

####transform bsc shapefile for leaflet

bsc<-st_transform(bsc, CRS('+proj=longlat +datum=WGS84'))

####Add XY coordinates to bsc spatial df

## find centroid coordinates
bsc_cnt = st_centroid(bsc)
bsc_crd = data.frame(st_coordinates(bsc_cnt))

#add ID column to each df and spatial df for joining
bsc$ID <- seq.int(nrow(bsc))
bsc_crd$ID <- seq.int(nrow(bsc_crd))

##join spatial frame with data frame to get the XY columns into the spatial frame

bsc<-geo_join(bsc, bsc_crd, 'ID', 'ID',
              how = "left")

#create label 
bsc_label<-paste(bsc$best_start)


#########################MAP###############################




######Define color palette and bins for map#######
library(leaflet)
library(RColorBrewer)

pal <- colorNumeric("PuRd",  domain = cepr_lac_childcare$childcare_tot)
#mybins <- c(0,10,20,50,100,500,Inf)


#######Map#########




leaflet(cepr_lac_childcare)%>%
  
  addMapPane("puma_pane", zIndex=485)%>%
  addMapPane("bsc_pane", zIndex=490)%>%
 
  
  #puma layer
  
  addPolygons(data=cepr_lac_childcare, weight = .40, color="black", smoothFactor = 0.8,
              opacity = 1, fillColor=~pal(childcare_tot), fillOpacity = .75,
              highlight=highlightOptions(color= "white", stroke = 1.5, weight = 2, bringToFront = TRUE), 
              popup = ~paste0(cepr_lac_childcare$name10, "</br>", "Total Child Care Workers: ",cepr_lac_childcare$childcare_tot),
               options = pathOptions(pane = "puma_pane")
              )%>%
  
  #bsc layer
  
  addPolygons(data=bsc, color="black", weight=2, opacity = 1, fill=F,
              label=as.character(bsc$best_start),
               options = pathOptions(pane = "bsc_pane")) %>%
  addLabelOnlyMarkers(data=bsc,  ~X, ~Y, label =  ~as.character(bsc_label), 
                      labelOptions = labelOptions(noHide= T, direction = 'top', textOnly = T,
                                                  style=list("font-size"="8px", "color"="black",  "font-weight" = "bold")))%>%
  
  
  #base and view
  addProviderTiles("CartoDB.PositronNoLabels")%>%
  setView(	-118.205914, 	34.187684	, zoom = 9)%>%
  
  #legend
  addLegend("bottomright", pal=pal, values = ~childcare_tot,
            title = "Child Care Workers Living<br>in Best Start Geographies")
  



```
Source: [Center for Economic and Policy Research Analysis of American Community Survey, 2014-2018 5-Year Estimate](https://github.com/ceprdata/frontline-workers)


# Internet Access 

In light of the pandemic, it is unsurprising that access to __internet and the digital divide__ has risen in importance. All Program Officers and Regional Network Grantees expressed the importance of digital equity in being able to outreach to families and for child care and education needs. 

14 out of 15 of the Best Start geographies have a lower rate of homes with internet access compared to the LA County rate at 82.4%. The exception to this is Palmdale, where homes have a rate of internet access that is closer to the county rate.

```{r}

#############Internet Access#################

internet<-dbGetQuery(con, "SELECT * FROM f5la_2021_internet")%>%
  filter(!grepl("LA County", best_start))

#highcharts

hc<-hchart(internet, "column",
         hcaes(x=best_start, y=pct_internet),
          tooltip = list(pointFormat = "Percentage of Households Internet: {point.pct_internet:.1f}%<br>
                         Number of Households Internet: {point.tot_internet}"))%>%

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""), 
             labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=100,
       plotLines = list(
      list(
        label = list(text = "LA County = 84.5%<br>", align = "left"),
        color = "#FF0000",
        width = 2,
        value = 84.5
      )
    ))%>%
    hc_title(
    text = "Homes with Internet Access in Best Start Geographies",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://data.census.gov/cedsci/">ACS 2018 5-Year Estimates (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)


# #create factors for the x axis labels (bsc) to customize the order
# internet$best_start <-  factor(internet$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# 
# cols<-c( "#FF6666", "#FF6666", "#FF6666","#FF6666", "#FF6666", "#FF6666","#FF6666","#FF6666","#FF6666",
#          "#FF6666","#FF6666","#FF6666","#FF6666","#FF6666")

#ggplot graph

# ggplot(internet, aes(y=pct_internet/100, x=best_start))+
#   geom_bar(stat="identity", fill = cols)+ 
#   geom_hline(yintercept=.824, linetype="dashed")+ #y intercept is the total rate which you can find on rc site, pgadmin, or from earlier table prior to filtering
#   geom_text(data=data.frame(x=0,y=.824), aes(x, y), label="LA County Rate = 82.4%",  vjust=-.5, hjust=-.1)+ 
#    scale_y_continuous(name="", limits = c(0, 1), labels=percent)+
#   scale_x_discrete(name="")+
#   theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         legend.title = element_blank())+
#   ggtitle("Homes with Internet Access in the Best Start Geographies")


``` 
<br>Source: 2019 ACS 5-Year Estimates

# Families who Own One or More Technology Devices

Remote learning and child care requires families to have reliable internet as well as sufficient devices for all the children and adults who are learning or working remotely from home. The visual below shows the percentage of families who own at least one or more devices at home. 

```{r}

#highcharts

hc<-hchart(internet, "column",
         hcaes(x=best_start, y=pct_oneormoredevice),
          tooltip = list(pointFormat = "Percentage of Homes w/ One or More Device: {point.pct_oneormoredevice:.1f}%<br>
                         Number of Households w/ One or More Device: {point.tot_oneormoredevice}"))%>%

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""), 
             labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=100,
       plotLines = list(
      list(
        label = list(text = "LA County =92.0%<br>", align = "left"),
        color = "#FF0000",
        width = 2,
        value = 92.0
      )
    ))%>%
    hc_title(
    text = "Homes with Internet Access in Best Start Geographies",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://data.census.gov/cedsci/">ACS 2019 5-Year Estimates (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)



```
<br>Source: 2019 ACS 5-Year Estimates

# Pre-K Early Learning Care Enrollment

The difference between the numbers of pre-k children who are eligible for subsidized early learning care programs versus enrolled in them is significant. This highlights the need to improve outreach and understand the barriers preventing eligible families from enrollment.<br>

```{r}

#####prek

#grab data
prek<-dbGetQuery(con, "SELECT * FROM bsc_unmet_ece_prek_new")


#convert data wide to long and prep for graphing

prek_long <- melt(setDT(prek), id.vars = c("best_start"), variable.name = "type")%>%
  filter(!grepl("unmet_need", type))%>%
  filter(!grepl("LA County", best_start))

prek_long<-prek_long%>%
  mutate(variable = ifelse(type %in% 'eligible_children_prek', 'Eligible Children',
                                ifelse(type %in% 'enrolled_children_prek', 'Enrolled Children',
                                       "Total Children")))




#highcharts
hc<-hchart(prek_long, "column",
         hcaes(x=best_start, y=value, group=variable),
         stacking="normal",
          tooltip = list(pointFormat = "Total: {point.value}"))%>%
      
      hc_tooltip(crosshairs = TRUE)%>%
  
  hc_colors(cols3)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""))%>%
    hc_title(
    text = "Pre-K Eligibility and Enrollment in Subsidized Early Learning Care Programs",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://elneedsassessment.org/">Early Learning Needs Assessment Tool, American Institutes for Research (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)
# 
# 
# #create factors for the x axis labels (bsc) to customize the order
# prek_long$best_start <-  factor(prek_long$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# 
# #graph
# 
# ggplot(prek_long, aes(fill=type, y=value, x=best_start))+
#   geom_bar(position="stack", stat="identity")+
#    scale_y_continuous(name="", labels=comma, limits = c(0, 30000))+
#   scale_x_discrete(name="")+
#         theme(plot.title = element_text(hjust = 0.5), legend.position="right", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         plot.margin = margin(.1, .1, .1, .1, "cm"))+
#   scale_fill_discrete(labels=c("Total", "Eligible", "Enrolled"))+
#   labs(fill="")+
#     ggtitle("Pre-K Eligibility and Enrollment in Subsidized \nEarly Learning Care Programs")
  

#graph LA County or make table???

# prek_la<-melt(setDT(prek), id.vars = c("bsc"), variable.name = "type")%>%
#   filter(grepl("LA County", bsc))
```
<br>Source: [Early Learning Needs Assessment Tool, American Institutes for Research](https://elneedsassessment.org/)

# Infant Toddler Early Learning Care Enrollment

The gap between infant toddlers who are eligible for subsidized early learning programs versus enrollment in them is substantial. Enrollment if extremely low across Best Start geographies. The gap for infant toddlers is larger than the gap among pre-k children, making this a higher priority area.<br>

```{r}

#grab data
it<-dbGetQuery(con, "SELECT * FROM bsc_unmet_ece_it_new")


#convert data wide to long and prep for graphing
it_long <- melt(setDT(it), id.vars = c("best_start"), variable.name = "type")%>%
  filter(!grepl("unmet_need", type))%>%
  filter(!grepl("LA County", best_start))


#mutate and make the labels nicer for the legend on the graph

it_long<-it_long%>%
  mutate(variable = ifelse(type %in% 'eligible_children_it', 'Eligible Children',
                                ifelse(type %in% 'enrolled_children_it', 'Enrolled Children',
                                       "Total Children")))


#highcharts graph
hc<-hchart(it_long, "column",
         hcaes(x=best_start, y=value, group=variable),
         stacking="normal",
          tooltip = list(pointFormat = "Total: {point.value}"))%>%
      
      hc_tooltip(crosshairs = TRUE)%>%
  hc_colors(cols3)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
    hc_yAxis(title = list(text = ""))%>%
    hc_title(
    text = "Infant Toddler Eligibility and Enrollment in Subsidized Early Learning Care Programs",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="https://elneedsassessment.org/">Early Learning Needs Assessment Tool, American Institutes for Research (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)



# #creat factors for the x axis labels (bsc) to customize the order
# it_long$best_start<- factor(it_long$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# #graph
# 
# ggplot(it_long, aes(fill=type, y=value, x=best_start))+
#   geom_bar(position="stack", stat="identity")+
#    scale_y_continuous(name="", labels=comma, limits=c(0, 30000))+
#   scale_x_discrete(name="")+
#         theme(plot.title = element_text(hjust = 0.5), legend.position="right", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         plot.margin = margin(.1, .1, .1, .1, "cm"))+
#   scale_fill_discrete(labels=c("Total", "Eligible", "Enrolled"))+
#   labs(fill="")+
#     ggtitle("Infant Toddler Eligibility and Enrollment in Subsidized \nEarly Learning Care Programs")


##if we want an LA only graph or table here ???

# it_la<-melt(setDT(it), id.vars = c("bsc"), variable.name = "type")%>%
#   filter(grepl("LA County", bsc))


```
<br>Source: [Early Learning Needs Assessment Tool, American Institutes for Research](https://elneedsassessment.org/)
