---
title: "Health Care"
output:
  html_document:
    number_sections: no
    theme: sandstone
    css: styles.css
    toc: yes
    toc_depth: 2
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '2'
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
 body{
  font-family: Franklin Gothic;
}
</style>


```{r setup, include=FALSE} 

knitr::opts_chunk$set(comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE
)

setwd("W:/Project/RDA Team/First5LA/V2.0 Report/R")

library(ggplot2)
library(dplyr)
library(stringr)
library(RPostgreSQL)
library(tidyr)
library(scales)
library(knitr)
library(data.table)
library(sp)
library(sf)
library(rgdal)
library(rpostgis)
library(highcharter)
library(kableExtra)
library(tigris)

# Data Setup
pw <- {
  "password"
}
# loads the PostgreSQL driver
drv <- dbDriver("PostgreSQL")

con <- dbConnect(drv, dbname = "f5la_v2",
                 host = "aws-postgres-db.c5udgz7ro8hq.us-west-2.rds.amazonaws.com", port = 5432,
                 user = "postgres", password = pw)

```


```{r, include=FALSE}

####### ESTABLISH HIGHCHART THEME ############


##colors as a vector

cols=c("#033E8C", "#EC098D", "#04B2D9","#26BFB0", "#64BF4B")

cols3=c("#033E8C", "#EC098D", "#04B2D9")

cols7=c("#6c3e96", "#ab3890", "#dc397b", "#fc515d","#033E8C","#ff793a", "#ffa600")

####MAKE MY HC THEME###

  thm <- hc_theme(
  colors = c("#033E8C", "#EC098D", "#04B2D9","#26BFB0", "#64BF4B"),
  chart = list(
    backgroundColor = ""
  ),
  title = list(
    style = list(
      color = "#333333",
      fontFamily = "Franklin Gothic Condensed"
    )
  ),
  subtitle = list(
    style = list(
      color = "#666666",
      fontFamily = "Franklin Gothic"
    )
  ),
  legend = list(
    itemStyle = list(
      fontFamily = "Franklin Gothic",
      color = "black"
    ),
    itemHoverStyle = list(
      color = "gray"
    )
  )
)


```

# Interview Findings

* Many families in Best Start geographies have a more difficult time accessing healthcare. This disparity creates greater challenges during Covid-19 as families lack access to testing.
* These indicators are the Impact Framework Prenatal Care, Postpartum Care, and Maternal Depression indicators. Progress on them helps achieve [<nobr style="color: #FF6699;">__First 5 LA’s Result: Early Intervention.__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)
* Several of the Best Start Community Change Agendas lift up Maternal Health as a community priority.

# Policy Opportunities {.tabset .tabset-pills}

## Systems Change

* __Improve the continuum of care to ensure that all children live as members of committed, nurturing, and permanent families.__ Services and supports provided to the child or youth and their family are tailored toward the goal of returning the child home whenever possible or to a permanent family through adoption or guardianship. Work to improve wraparound community-based social and health services (and navigation to those services) for people released from incarceration and their families. Increase reliance on culturally competent, non-physician health professionals and community health workers (e.g., midwives, promotoras) for maternal (pre- and post-natal) care via scope of practice reforms. [<nobr style="color: #04B2D9;">__F5LA Result: Family Resources__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74) [<nobr style="color: #033E8C;">__F5LA Result: Child Safety __</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)

## Infrastructure to Support Children and Families

* __Bridge the digital divide in highest-need areas to ensure that children and families of essential workers have access to telehealth for preventative health and wellness care.__ Build private-public partnerships to ensure all families have access to reliable internet connectivity and technology so that they can participate in health and mental health services in the safety of their homes.[<nobr style="color: #04B2D9;">__F5LA Result: Family Resources__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)

## Direct Services and Technical Support

* __Disinvest from law enforcement in potential child abuse situations.__ Ensure that in-person checks on children considered “high-risk” for abuse are conducted by social service, rather than law enforcement personnel. [<nobr style="color: #333366;">__F5LA Result: Child Safety __</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74) [<nobr style="color: #04B2D9;">__F5LA Result: Family Resources__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)
* __Expand access to essential health care services. Set a baseline standard requiring that every resident in LA receive primary care and require county programs to extend eligibility regardless of immigration status.__ Provide resources for COVID-19 testing and follow up care at local community health clinics [<nobr style="color: #04B2D9;"> __F5LA Result: Family Resources__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74) [<nobr style="color: #333366;">__F5LA Result: Child Safety __</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74) [<nobr style="color: #04B2D9;">__F5LA Result: Family Resources__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)
* __Support culturally appropriate health promotion and community ownership for essential workers.__ Support Worker Public Health Councils to ensure workers have a say in implementing safety measures to prevent COVID outbreaks. Increase investments supporting community health promotion and education .[<nobr style="color: #333366;">__F5LA Result: Child Safety __</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74) [<nobr style="color: #04B2D9;">__F5LA Result: Family Resources__</nobr>](https://teams.microsoft.com/l/file/7BCF9E27-DD6A-442D-BD86-AF6566D0C38B?tenantId=abc23eed-8c00-4a99-892a-09219a95119e&fileType=pdf&objectUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject%2FShared%20Documents%2FGeneral%2Fresults_for_children_and_families.pdf&baseUrl=https%3A%2F%2Ffirst5lacounty.sharepoint.com%2Fsites%2FAdvancementProject&serviceName=teams&threadId=19:1e7e7b70c7eb4cb6b2e851e41582db4f@thread.skype&groupId=1f9a4169-31de-476b-a42f-e2f7da7fce74)

# Uninsured Population

Southeast LA and Panorama City & Neighbors both have the highest number of uninsured households and have among the highest number of total households within the Best Start geography.

```{r}

#grab data
insure<-dbGetQuery(con, "SELECT * FROM f5la_2021_insurance")%>%
  filter(!grepl('LA County', best_start))


#separate the estimate and percents to separate columns then recombine 

insure_num<-gather(insure, num_measure, num_value,  total_uninsured:pct_whitealone_uninsured, factor_key=TRUE)%>%
  filter(grepl("total", num_measure))

insure_pct<-gather(insure, pct_measure, pct_value, total_uninsured:pct_whitealone_uninsured, factor_key=TRUE)%>%
  filter(grepl("pct", pct_measure))

#combine pct and number dfs
insure_long<-cbind(insure_num, insure_pct)

#remove duplicate name  column (best_start)
insure_long<-insure_long[c(-4)]

#now create a nicer 'variable' column for grouping the races

insure_long<-insure_long%>%
 mutate(variable=ifelse(pct_measure %in% 'pct_whitealone_uninsured', 'Percent White',
                         ifelse(pct_measure %in% 'pct_black_uninsured', 'Percent Black',
                                ifelse(pct_measure %in% 'pct_aian_uninsured', 'Percent AIAN',
                                       ifelse(pct_measure %in% 'pct_asian_uninsured', 'Percent Asian',
                                         ifelse(pct_measure %in% 'pct_nhpi_uninsured', 'Percent Native Hawaiin/Pacific Islander',
                                                ifelse(pct_measure %in% 'pct_latinxcombo_uninsured', 'Percent Latinx', ifelse(pct_measure %in% 'pct_twoormore_uninsured', 'Percent Two or More Races', ifelse(pct_measure %in% "pct_other_uninsured", 'Percent Other Race', "Blank"))))))))) 

#we can remove the 'total insured' measure and percent as well
insure_long_notot<-insure_long%>%
  filter(!grepl('Blank', variable))

#highcharts

hc<-hchart(insure_long_notot, "column",
         hcaes(x=best_start, y=pct_value, group=variable),
         stacking='normal',
          tooltip = list(pointFormat = "Percent Uninsured: {point.pct_value:,.f}%<br>
                         Total Uninsured: {point.num_value}"))%>%
      
      hc_tooltip(crosshairs = TRUE)%>%
  
  #hc_colors(cols7)%>%
     
     hc_xAxis(title = list(text = ""),
               categories=c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))%>%
  
    hc_yAxis(title = list(text = ""),
             labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=.5) %>%
  
    hc_title(
    text = "Uninsured Population by Best Start Geography",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
  
      hc_subtitle(
    text =  '<a href="https://data.census.gov/cedsci/">ACS 2019 5-Year Estimates (Click to download)</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)



# #create factors for the x axis labels (bsc) to customize the order
# insure_long$best_start <-  factor(insure_long$best_start,levels = c("East LA", "Metro LA", "South El Monte/El Monte", "Southeast LA", "Broadway/Manchester", "Compton/East Compton", "Watts/Willowbrook", "West Athens", "North East Valley", "Panorama City & Neighbors", "Central Long Beach", "Wilmington", "Lancaster", "Palmdale"))
# 
# #graph
# 
# ggplot(insure_long, aes(fill=factor(measure), y=value, x=best_start))+
#   geom_bar(position="stack", stat="identity")+
#   theme(plot.title = element_text(hjust = 0.5), 
#               legend.position="right", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         plot.margin = margin(.1, .1, .1, .1, "cm"))+
#    scale_y_continuous(name="", labels=comma)+
#    scale_x_discrete(name="")+
#   
#         theme(plot.title = element_text(hjust = 0.5), 
#               legend.position="right", axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         plot.margin = margin(.1, .1, .1, .1, "cm"))+
#   
#   scale_fill_discrete(labels=c("Total Households", "Total Uninsured"))+
#   
#   labs(fill="")+
#  
#     ggtitle("Uninsured Population")

```
<br>Source: ACS 2019 5-Year Estimates

# Postpartum Care

A high percentage of mothers across the five supervisorial districts received postpartum check-ups. These successful figures speak to the growing degree of access to maternal healthcare services across the county.<br>

```{r}

#grab data 
postpartum<-dbGetQuery(con, "SELECT * FROM lamb_postpartum_check_supdist_2016")

#remove the 'total' row because we will plot it as a y intercept line to match other graphs
postpartum<-postpartum%>%
  filter(!grepl('Los Angeles County', bos_name))

#highchart

hc<-hchart(postpartum, "column",
         hcaes(x=bos_name, y=total_pct),
          tooltip = list(pointFormat = "Percent: {point.total_pct:.1f}%"))%>%
      

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = "Supervisorial Districts"))%>%
    hc_yAxis(title = list(text = ""), 
              labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")),
       plotLines = list(
      list(
        label = list(text = "LA County = 90.7%", align = "left"),
        color = "#FF0000",
        width = 2,
        value = 90.7,
        zIndex=5
      )
    ))%>%
    hc_title(
    text = "Annual Percentage of Mothers Who Had a Postpartum Check-Up",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="http://publichealth.lacounty.gov/mch/lamb/LAMB.html">Los Angeles County Department of Public Health Los Angeles Mommy and Baby Project</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)



#set colors 
# 
# cols<-c( "#FF6666", "#FF6666", "#FF6666","#FF6666", "#FF6666", "#5dbcd2")
# 
# 
# #graph
# 
# ggplot(postpartum, aes(y=total_pct/100, x=bos_id, label=total_pct))+
#   geom_bar(stat="identity", fill = cols)+ 
#   geom_text(aes(label=paste0(total_pct, "%")), size = 3, position = position_stack(vjust = 0.5))+
#    scale_y_continuous(name="", limits = c(0, 1), labels=percent)+
#   scale_x_discrete(name="\nSupervisorial Districts", labels=c("LA County", "District 1", "District 2", "District 3", "District 4", "District 5"))+
#   theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         legend.title = element_blank())+
#   ggtitle("Annual Percentage of Mothers Who Had a Postpartum Check-Up")
  
  
```
<br>Source: Los Angeles County Department of Public Health Los Angeles Mommy and Baby Project (LAMB Survey)

# Maternal Depression

The percentage of mothers who experienced prenatal or postpartum depression across the five supervisorial districts closely resembles the county percentage. There is also minimal variation between the five districts.<br>

```{r}

#grab data 
depression<-dbGetQuery(con, "SELECT * FROM lamb_maternal_depression_supdist_2016")

#remove the 'total' row because we will plot it as a y intercept line to match other graphs
depression<-depression%>%
  filter(!grepl('LA County', bos_name))

#highchart

hc<-hchart(depression, "column",
         hcaes(x=bos_name, y=pct_total),
          tooltip = list(pointFormat = "Percent: {point.pct_total:.1f}%<br>
                         Number: {point.num_total}"))%>%
      

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = "Supervisorial Districts"))%>%
    hc_yAxis(title = list(text = ""), 
              labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=100,
       plotLines = list(
      list(
        label = list(text = "LA County = 25.2%", align = "left"),
        color = "#FF0000",
        width = 2,
        value = 25.2,
        zIndex=5
      )
    ))%>%
    hc_title(
    text = "Annual Percentage of Mothers Who Experienced Prenatal or Postpartum Depression",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="http://publichealth.lacounty.gov/mch/lamb/LAMB.html">Los Angeles County Department of Public Health Los Angeles Mommy and Baby Project</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)
# 
# #set colors 
# 
# cols<-c("#5dbcd2", "#FF6666", "#FF6666", "#FF6666","#FF6666", "#FF6666")
# 
# 
# #graph
# ggplot(depression, aes(y=pct_total/100, x=bos_id))+
#   geom_bar(stat="identity", fill = cols)+ 
#     geom_text(aes(label=paste0(pct_total, "%")), size = 3, position = position_stack(vjust = 0.5))+
#    scale_y_continuous(name="", limits = c(0, 1),labels=percent)+
#   scale_x_discrete(name="\nSupervisorial Districts", labels=c("LA County", "District 1", "District 2", "District 3", "District 4", "District 5"))+
#   theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         legend.title = element_blank())+
#   ggtitle("Annual Percentage of Mothers Who Experienced \nPrenatal or Postpartum Depression")
  
```
<br>Source: Los Angeles County Department of Public Health Los Angeles Mommy and Baby Project (LAMB Survey)


# Prenatal Care

The annual percentage of mothers who entered prenatal care after the 1st trimester of pregnancy is low across the five supervisorial districts and in the county. Supervisorial district 3 has the lowest percent at 5.8%. This district encompasses Pacoima and Panorama City.<br>

```{r}

#grab data 
prenatal<-dbGetQuery(con, "SELECT * FROM lamb_prenatal_care_supdist_2016")

#remove the 'total' row because we will plot it as a y intercept line to match other graphs
prenatal<-prenatal%>%
  filter(!grepl('Los Angeles County', bos_name))

#highchart

hc<-hchart(prenatal, "column",
         hcaes(x=bos_name, y=pct_total),
          tooltip = list(pointFormat = "Percent: {point.pct_total:.1f}%<br>
                         Number: {point.num_total}"))%>%
      

      hc_tooltip(crosshairs = TRUE)%>%
     
     hc_xAxis(title = list(text = "Supervisorial Districts"))%>%
    hc_yAxis(title = list(text = ""), 
              labels = list(
      formatter = JS("function () {
                      return Math.abs(this.value) + '%';
                                    }")), min=0,max=20,
       plotLines = list(
      list(
        label = list(text = "LA County = 8.2%", align = "left", y=-20),
        color = "#FF0000",
        width = 2,
        value = 8.2,
        zIndex=5
      )
    ))%>%
    hc_title(
    text = "Annual Percentage of Mothers Who Who Entered Prenatal Care After 1st Trimester of Pregnancy",
    margin = 20,
    align = "left",
    style = list(useHTML = TRUE, fontWeight="bold")
    )%>%
      hc_subtitle(
    text =  '<a href="http://publichealth.lacounty.gov/mch/lamb/LAMB.html">Los Angeles County Department of Public Health Los Angeles Mommy and Baby Project</a>',
     style = list( fontWeight = "bold"),
    align = "left"
  )%>%
     hc_legend(enabled = TRUE) 

hc_add_theme(hc, thm)

#set colors 
# 
# cols<-c("#FF6666", "#FF6666", "#FF6666","#FF6666", "#FF6666", "#5dbcd2")
# 
# #graph
# ggplot(prenatal, aes(y=pct_total/100, x=bos_id))+
#   geom_bar(stat="identity", fill = cols)+ 
#       geom_text(aes(label=paste0(pct_total, "%")), size = 3, position = position_stack(vjust = 0.5))+
#    scale_y_continuous(name="", limits = c(0, .25), labels=percent)+
#   scale_x_discrete(name="\nSupervisorial Districts", labels=c("LA County", "District 1", "District 2", "District 3", "District 4", "District 5"))+
#   theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
#         legend.title = element_blank())+
#   ggtitle("Annual Percentage of Mothers Who Entered Prenatal Care \nAfter 1st Trimester of Pregnancy")


```
<br>Source: Los Angeles County Department of Public Health Los Angeles Mommy and Baby Project (LAMB Survey)